Comparing binsegRcpp with other implementations of binary segmentation for changepoint detection

### 2025-05-02 article.Rnw
figure 1 update

\begin{table}[t!]
\centering
\begin{tabular}{l|ccccc}
  package & binsegRcpp & changepoint & wbs & fpop & ruptures \\
  function & binseg & cpt.mean & sbs & multiBinSeg & Binseg \\
%   > ruptures$version$version
% [1] "1.1.6"
% > sapply(c("binsegRcpp", "changepoint", "wbs", "fpop"), function(p)paste(packageVersion(p)))
%  binsegRcpp changepoint         wbs        fpop 
% "2022.3.29"     "2.2.3"       "1.4" "2019.8.26"
% https://github.com/HaotianXu/changepoints does not have binary segmentation.
  version & 2022.3.29 & 2.2.3 & 1.4 & 2019.8.26 & 1.1.6\\
\hline
  weights & yes & no & no & no & no \\
  max segs & yes & yes & no & yes & yes \\
  dim & one & one & one & multi & multi \\
  correct & yes & no & yes & yes & no \\
  losses & 5 & 6 & 1 & 1 & 10 \\
  language & C++ & C & C & C++ & Python \\
  % all propose some loss computation.
  storage & STL multiset & arrays & recursion & heap & LRU cache \\
  space & $O(S)$ & $O(S^2)$ & $O(S)$ & $O(S)$ & $O(S)$ \\
  cumsum & yes & yes & yes & yes & no \\
  best & $O(N\log N)$ & $O(N^3)$ & $O(N\log N)$ & $O(N\log N)$ & $>O(N\log N)$ \\
  worst & $O(N^2)$ & $O(N^3)$ & $O(N^2)$ & $O(N^2)$ & $O(N^2)$ \\
  CV & yes & no & no & no & no\\
  params & yes & largest & no & no & no \\
\end{tabular}
\caption{\label{tab:overview}
  Properties (rows) of five binary segmentation libraries (columns).
Properties are weights (can specify observation-specific positive weights for the loss), max segs (can specify maximum number of segments parameter), dim (dimensions of input data), correct (does code return correct model parameters?), losses (number of loss functions implemented), language (programming language to implement loss), storage (technique used to store cost of splitting a segment), space (space complexity in number of segments $S$), cumsum (cumulative sum used), best (time complexity in best case data), worst (time complexity in worst case data), CV (support for cross-validation), params (parameters are returned). }
\end{table}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\textwidth]{figure-neuroblastoma.png}
  \caption{\label{fig:neuroblastoma} For a real cancer DNA copy number
    data set with 273 observations, we show the first four
    changepoints detected by several different implementations of
    binary segmentation.}
\end{figure}

>>>>

\begin{table}[t!]
\centering
\begin{tabular}{l|ccccc}
  package & binsegRcpp & changepoint & wbs & fpop & ruptures \\
  function & binseg & cpt.mean & sbs & multiBinSeg & Binseg \\
%   > ruptures$version$version
% [1] "1.1.6"
% > sapply(c("binsegRcpp", "changepoint", "wbs", "fpop"), function(p)paste(packageVersion(p)))
%  binsegRcpp changepoint         wbs        fpop 
% "2022.3.29"     "2.2.3"       "1.4" "2019.8.26"
% https://github.com/HaotianXu/changepoints does not have binary segmentation.
  version & 2022.3.29 & 2.2.3 & 1.4 & 2019.8.26 & 1.1.9\\
\hline
  weights & yes & no & no & no & no \\
  max segs & yes & yes & no & yes & yes \\
  dim & one & one & one & multi & multi \\
  correct & yes & no & yes & yes & yes \\
  losses & 5 & 6 & 1 & 1 & 10 \\
  language & C++ & C & C & C++ & Python \\
  % all propose some loss computation.
  storage & STL multiset & arrays & recursion & heap & LRU cache \\
  space & $O(S)$ & $O(S^2)$ & $O(S)$ & $O(S)$ & $O(S)$ \\
  cumsum & yes & yes & yes & yes & no \\
  best & $O(N\log N)$ & $O(N^3)$ & $O(N\log N)$ & $O(N\log N)$ & $>O(N\log N)$ \\
  worst & $O(N^2)$ & $O(N^3)$ & $O(N^2)$ & $O(N^2)$ & $O(N^2)$ \\
  CV & yes & no & no & no & no\\
  params & yes & largest & no & no & no \\
\end{tabular}
\caption{\label{tab:overview}
  Properties (rows) of five binary segmentation libraries (columns).
Properties are weights (can specify observation-specific positive weights for the loss), max segs (can specify maximum number of segments parameter), dim (dimensions of input data), correct (does code return correct model parameters?), losses (number of loss functions implemented), language (programming language to implement loss), storage (technique used to store cost of splitting a segment), space (space complexity in number of segments $S$), cumsum (cumulative sum used), best (time complexity in best case data), worst (time complexity in worst case data), CV (support for cross-validation), params (parameters are returned). }
\end{table}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\textwidth]{changepoint.bug.png}
  \caption{\label{fig:neuroblastoma} For a real cancer DNA copy number
    data set with 273 observations, we show the first four
    change-points models for two different R packages that provide code for
    binary segmentation: \pkg{binsegRcpp} and \pkg{changepoint}.}
\end{figure}
